---
title: "lab3"
author: "Ashwath Raj"
date: "September 2, 2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(tidyverse)
library(R.utils)
library(leaflet)
library(readr)
library(lubridate)
```

```{r}
download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
              "met_all.gz", method="libcurl", timeout = 60)
met <- data.table::fread("met_all.gz")

```

```{r}
#2
dim(met)
head(met)
tail(met)
```


```{r}
#3
str(met)
```

###4
- It looks like the elevation variable has observations with 9999.0, which is probably an indicator for missing. We should take a deeper look at the data dictionary to confirm. The wind speed variable is ok but there are a lot of missing data.

- After checking the data we should make the appropriate modifications. Replace elevations with 9999 as NA.

- At what elevation is the highest weather station?
  The highest elevation is 4113 meters

- We also have the issue of the minimum temperature being -40C, so we should remove those observations.

- We again notice that there is a -17.2C temperature reading that seems suspicious.

```{r}
summary(met[,8:13])
# dim(met[is.na(temp)])[1]/dim(met)[1]
met[met$elev==9999.0] <- NA
summary(met$elev)

met2 <- met[temp> -15]
summary(met$temp)
met2 <- met[order(temp)]
head(met2)
```

  
###5 (see above for change to temp > -15)
 - I used these value to identify unusual temps and their lat,longs
```{r}
# met[temp < -15]
head(met2)
```

###6 Summary Stats
  - It appears that temp is most closely correlated to the hour
```{r}
elev <- met[elev == max(elev)]

cor(elev$temp, elev$wind.sp, use = "pairwise.complete.obs")
cor(elev$temp, elev$hour, use = "pairwise.complete.obs")
cor(elev$temp, elev$day, use = "pairwise.complete.obs")
```

###7 Exploratory Graphs
  - temp vs. date has regular cycles, but temp and wind speed seems more erratic with switching positive and negative trends across 5+ day cycles.
```{r}
hist(met$elev)
hist(met$temp)
hist(met$wind.sp)


elev$date <- with(elev, ymd_h(paste(year,month,day,hour,sep=' ')))
summary(elev$date)

leaflet(elev) %>%
  addProviderTiles('Esri.WorldImagery') %>%
  addCircles(lat =~ lat, lng=~lon, opacity =1, fillOpacity =1, radius = 100)
```

```{r}
plot(elev$date, elev$temp, type = 'l')
plot(elev$date, elev$wind.sp, type = 'l')
```


