---
output: 
  html_document: 
    fig_height: 10
    fig_width: 5
    theme: cerulean
---
\---
title: "Lab 01: Hello R"
author: "Ashwath Raj"
date: "8/19/2020"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

#install.packages(c("tidyverse", "datasauRus"))
library(tidyverse)
library(datasauRus)
```

## Exercise 1

```{r}
datasaurus_dozen %>%
  count(dataset)

nrow(datasaurus_dozen)
ncol(datasaurus_dozen)
```

datasaurus_dozen has 1846 rows and 3 cols
The variables are dataset, x, and y.

## Exercise 2

```{r fig.height=3, fig.width=3}


dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
dino_data %>% 
  summarize (r = cor(x,y))



```
r = -0.06447185	




## Exercise 3

```{r fig.height=3, fig.width=3}

star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
star_data %>% 
  summarize (r = cor(x,y))
```

r = -0.0629611
r is slightly more positively correlated for the star dataset than the dino dataset

## Exercise 4

```{r fig.height=3, fig.width=3}

circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
circle_data %>% 
  summarize (r = cor(x,y))
```

r = -0.06834336
r is slightly less positively correlated for the star dataset than the dino dataset

## Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))

```
